Binary companions of red giant stars with APOGEE DR14

### 2018-02-25 paper/1-catalog/twoface-catalog.tex
More TODO items
fix unclosed todo
fix two undefined

\newcommand{\nprior}{536,870,912}
\newcommand{\nposterior}{256}
\newcommand{\nstars}{96,231}
\newcommand{\nvisits}{397,559}

@@

\begin{abstract}\noindent % trust me
% Context
Repeat radial-velocity measurements of stars can be used to identify stellar,
sub-stellar, and planetary-mass companions.
Even sparse or few-epoch observations are useful for detecting companions,
though such data are difficult to use for measuring physical properties of
individual systems because permitted orbital solutions can be highly degenerate.
% Aims
Using a custom-built Monte Carlo sampler (\thejoker) to deliver (often highly
multi-modal) posterior beliefs about companion orbital parameters, here we
perform a search for secondary companions of over 100,000 stars observed by the
\apogee\ survey (\DR) with $\geq 3$ epochs.
% Methods
We select stars with probable companions by \todo{how?}.
% Results
We provide (1) a catalog of \ncompanions\ companions for which the companion
properties can be confidently determined, (2) a catalog of stars that likely
have companions, but for  which more observations are needed to uniquely
determine the orbital properties, and (3) posterior samplings for all \ntotal\
stars in the parent sample.
We highlight interesting systems and show the characteristics of stars with
confidently determined companion properties.
\end{abstract}

@@

>>>>

\newcommand{\nprior}{536,870,912}
\newcommand{\nposterior}{256}
\newcommand{\nstars}{96,231}
\newcommand{\nvisits}{397,559}
\newcommand{\ncompanions}{xx}

@@

\begin{abstract}\noindent % trust me
% Context
Repeat radial-velocity measurements of stars can be used to identify stellar,
sub-stellar, and planetary-mass companions.
Even sparse or few-epoch observations are useful for detecting companions,
though such data are difficult to use for measuring physical properties of
individual systems because permitted orbital solutions can be highly degenerate.
% Aims
Using a custom-built Monte Carlo sampler (\thejoker) to deliver (often highly
multi-modal) posterior beliefs about companion orbital parameters, here we
perform a search for secondary companions of over 100,000 stars observed by the
\apogee\ survey (\DR) with $\geq 3$ epochs.
% Methods
We select stars with probable companions by \todo{how?}.
% Results
We provide (1) a catalog of \ncompanions\ companions for which the companion
properties can be confidently determined, (2) a catalog of stars that likely
have companions, but for  which more observations are needed to uniquely
determine the orbital properties, and (3) posterior samplings for all \nstars\
stars in the parent sample.
We highlight interesting systems and show the characteristics of stars with
confidently determined companion properties.
\end{abstract}

@@

\todo{Period - eccentricity plot? Tidal circularization (See "Debug MCMC
continue")}

\todo{Stars with Martig or Ness masses - m2min}
